---
title: "Data Science with R Programming"
author: "Sachin Sharma"
date: "August 24, 2021"
output:
  html_document: default
  word_document: default
---

```{r}

library(tidyverse)
library(datasets)
library(nycflights13)
head(flights)
```

### * int stan?s for integers.
### * dbl stands for doubles, or real numbers.
### * chr stands for character vectors, or strings.
### * dttm stands for date-times (a date + a time).
### * lgl stands for logical, vectors that contain only TRUE or FALSE.
### * fctr stands ?or factors, which R uses to represent categorical variables with fixed possible values.
### * date stands for dates.

## dplyr Basics
### We are going to learn the five key dplyr functions that allow you to solve the vast majority of your data-manipulation?challenges:
### .  Pick observations by their values **(filter())**.
### .  Reorder the rows **(arrange())**.
### .  Pick variables by their names **(select())**.
### .  Create new variables with functions of existing variables **(mutate())**.
### .  Colla?se many values down to a single summary **(summarize())**.

## These can all be used in conjunction with **group_by()**, which changes the scope of each function from operating on the entire dataset to operating on it group-by-group.

## Filter Rows with f?lter()
**filter() allows you to subset observations based on their values.**




```{r cars}
filter(flights, month == 1, day == 1)

```

## To save this data you can use a variable.

```{r }

df_1 =filter(flights, month == 1, day == 1)
print(df_1)

```
## ?n the above case you need to print the variable name after that you get the ouput , you can do it simultaneously by using the following code line : 

```{r }
(df_1 =filter(flights, month == 1, day == 1))
```
# Comparisons
## If you want to use filtering ef?ectively, you should know how to select the observations by using correct comparison operators viz : >, >=, <, <=, != (not equal), and == (equal).

## Logical Operators
### & is "and," | is "or," and ! is "not."



